\vspace{-15mm} \fontsize{24pt}{10pt}\selectfont \textbf{Traversing symmetric NAT with predictable port allocation function}

### 2013-12-19 paper_lncs.tex
lncs

\documentclass[twoside]{article}

@@

% ------
% Lettrines
\usepackage{lettrine}

@@

% ------
% Titling (section/subsection)
\usepackage{titlesec}
\renewcommand\thesection{\Roman{section}}
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}

% ------
% Header/footer
\usepackage{fancyhdr}
	\pagestyle{fancy}
	\fancyhead{}
	\fancyfoot{}
	\fancyhead[C]{SPW 2014 $\bullet$ Twenty-second International Workshop on Security Protocols}
	\fancyfoot[RO,LE]{\thepage}
% CFP: http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=33620&copyownerid=44118

@@

% ------
% Math
\usepackage{amsthm}
\usepackage{amsmath, mathtools}
\usepackage{fixltx2e}
% \usepackage{wrapfig}
\usepackage{tikz}
\usepackage{float}
\usepackage{multirow}
%\usepackage{appendices}

@@

\maketitle
\thispagestyle{fancy}

\begin{abstract}
\noindent Network Address Translators cause troubles for VoIP and other P2P services since central servers are needed for communication.
A presence of such potentially malicious hosts in a communication path is not desired, mainly due to increased cost, poor link quality 
and some security consequences.
Several solution exist for traversing NAT but symmetric case is still problematic. We propose algorithms using single source port for 
symmetric NAT traversal, each with different properties and applicability. 
Paper gives a theoretic point of view on the NAT traversal problem by stating problem formally and modeling a network connected to 
NAT as a random process, in order to evaluate algorithms in a different settings.
% 
% ToDo; Will be written as the last part of the paper... Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur magna lorem, tempor sed facilisis vel, porta et turpis. Sed et felis a massa dictum posuere. Aliquam hendrerit rhoncus ipsum sit amet placerat. Duis fringilla est eu arcu mollis faucibus non sit amet eros. Vestibulum risus nibh, dapibus vitae laoreet eget, fringilla quis nisl. Proin consequat nibh sit amet mauris suscipit tincidunt. Sed rutrum, purus nec aliquam faucibus, quam libero venenatis nisi, ut tempor mi sapien vel diam. Pellentesque sagittis elit non risus malesuada accumsan. Morbi consequat urna.
\end{abstract}

\begin{multicols}{2}
% \lettrine[nindent=0em,lines=3]{L}orem ipsum dolor sit amet.

@@

Wang~\emph{et.~al.} \citep{Wang:2006:RSN:1156422.1156550} propose a NAT traversal algorithm for setting we are using based on
a changing of a source port, while our algorithms keep source port constant.

@@

\begin{figure}[H]
{\scalebox{0.43}{\includegraphics[trim=40 0 0 0]{alg_steps.pdf}}}
\caption{Steps of the algorithms needed to success on average w.r.t. $\lambda$. Algorithms denoted in a same way as in figure \ref{fig:alg_eval}.}
\label{fig:alg_steps}
\end{figure}
Figure \ref{fig:alg_eval} depicts algorithms success rate w.r.t. $\lambda$. 
Figure \ref{fig:alg_steps} depicts number of steps needed 
to succeed on average. From figures it is visible Alg. I is more suitable for networks with low 
workload since has $100\%$ success rate for $\lambda \in [0, 0.035]$. Outside this interval 
Alg. I is not working and another solution has to be applied. The problem is new connections are
created faster than algorithm progresses.

@@

\section{Conclusion}
The aim of this work was to study problem of the NAT traversal from statistical point of view,
and to provide an algorithm with high success rate for networks with low workload that is easy to 
implement and requires little system resource. 
Several algorithms solving this problem but there are still some open questions remaining.

@@

We developed an application written in Python that simulates NAT and mentioned algorithms, computes
statistics for port distributions on NAT and simulates algorithms for different parameters. It
may be helpful for another researchers interested in this area so we published it in public domain
hosted on github [URL:WHERE].

@@

\end{multicols}

\end{document}

>>>>

% \documentclass[twoside]{article}
\documentclass{llncs}
%\usepackage{llncsdoc}

@@

% ------
% Lettrines
% \usepackage{lettrine}

@@

% ------
% Titling (section/subsection)
% \usepackage{titlesec}
% \renewcommand\thesection{\Roman{section}}
% \titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{}

% ------
% Header/footer
% \usepackage{fancyhdr}
% 	\pagestyle{fancy}
% 	\fancyhead{}
% 	\fancyfoot{}
% 	\fancyhead[C]{SPW 2014 $\bullet$ Twenty-second International Workshop on Security Protocols}
% 	\fancyfoot[RO,LE]{\thepage}
% CFP: http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=33620&copyownerid=44118

@@

% ------
% Math
% \usepackage{amsthm}
\usepackage{amsmath, mathtools}
\usepackage{fixltx2e}
% \usepackage{wrapfig}
\usepackage{tikz}
\usepackage{float}
\usepackage{multirow}
%\usepackage{appendices}

@@

\maketitle
% \thispagestyle{fancy}

\begin{abstract}
\noindent Network Address Translators cause troubles for VoIP and other P2P services since central servers are needed for communication.
A presence of such potentially malicious hosts in a communication path is not desired, mainly due to increased cost, poor link quality 
and security consequences.
Several solution exist for traversing NAT but symmetric case is still problematic. We propose algorithms using single source port for 
symmetric NAT traversal, each with different properties and applicability. 
Paper gives a theoretic point of view on the NAT traversal problem by stating problem formally and modeling a network connected to 
NAT as a random process, in order to evaluate algorithms in a different settings.
% 
% ToDo; Will be written as the last part of the paper... Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur magna lorem, tempor sed facilisis vel, porta et turpis. Sed et felis a massa dictum posuere. Aliquam hendrerit rhoncus ipsum sit amet placerat. Duis fringilla est eu arcu mollis faucibus non sit amet eros. Vestibulum risus nibh, dapibus vitae laoreet eget, fringilla quis nisl. Proin consequat nibh sit amet mauris suscipit tincidunt. Sed rutrum, purus nec aliquam faucibus, quam libero venenatis nisi, ut tempor mi sapien vel diam. Pellentesque sagittis elit non risus malesuada accumsan. Morbi consequat urna.
\end{abstract}

% \begin{multicols}{2}
% \lettrine[nindent=0em,lines=3]{L}orem ipsum dolor sit amet.

@@

Wang~\emph{et.~al.} \citep{Wang:2006:RSN:1156422.1156550} propose a NAT traversal algorithm for setting we are using based on
a changing of a source port, while in our approach we want to explore possibilities with constant source port.

@@

\begin{figure}[H]
{\scalebox{0.43}{\includegraphics[trim=40 0 0 0]{alg_steps.pdf}}}
\caption{Steps of the algorithms needed to success on average w.r.t. $\lambda$. Algorithms denoted in a same way as in figure \ref{fig:alg_eval}.}
\label{fig:alg_steps}
\end{figure}
Figure \ref{fig:alg_eval} shows algorithms success rate w.r.t. $\lambda$. 
Figure \ref{fig:alg_steps} depicts number of steps needed 
to succeed on average. From figures it is visible Alg. I is more suitable for networks with low 
workload since has $100\%$ success rate for $\lambda \in [0, 0.035]$. Outside this interval 
Alg. I is not working and another solution has to be applied. The problem is new connections are
created faster than algorithm progresses.

@@

\section{Conclusion}
The aim of this work was to study problem of the NAT traversal from statistical point of view,
and to provide an algorithm with high success rate for networks with low workload that is easy to 
implement and requires little system resources. 
Several algorithms solving this problem were proposed but there are still some open questions remaining. 
Our goal was to find the algorithms that maximize success rate using only one source port strategies 
what can be used in further research, possibly in combination with previous multiple source port strategies.

@@

We developed an application written in Python that simulates NAT and mentioned algorithms, computes
statistics for port distributions on NAT and simulates algorithms for different parameters. It
may be helpful for another researchers interested in this area so we published it in public domain
hosted on GitHub [URL:HERE].

@@

% \end{multicols}
\end{document}
